SPARQL on the Open, Decentralised Web

### 2016-07-24 dissertation/problems.tex
rewrite microcontroller problem

Heterogeneity should also be expected in different types of servers
and clients, in particular

\begin{problem}\label{prob:microcontroller}
A client running on a microcontroller does not have significant
processing capability.
\end{problem}

>>>>

Heterogeneity should also be expected in different types of servers
and clients. In particular, microcontrollers and to a lesser extent,
mobile phones, are resource constrained devices. Thus:

\begin{problem}\label{prob:microcontroller}
Clients run on devices with a wide range of processing capability.
\end{problem}
